Manuscript

### 2014-12-07 inst/simulation/manuscript.Rmd
...

```{r figure-5-init}
getCIProportions <- function(scenarios, modelNames) {
  study <- getStudy(scenario="A")
  validation <- Validation(study=study, populationSizeOverEstimate=Inf)
  a <- validation$getValidatedCredibilityIntervalsProportions(scenarios=scenarios, modelNames=modelNames)
  b <- validation$getValidatedCredibilityIntervalsProportions(scenarios=scenarios, modelNames=modelNames, probs=c(.25, .75), probsName="50%")
  credibilityIntervals <- rbind(a, b)
  return(credibilityIntervals)  
}

plotCIProportions <- function(credibilityIntervals) {
  p <- ggplot(credibilityIntervals, aes(scenario, Proportion, shape=Interval, colour=modelName)) + geom_point() +
    scale_shape_manual(values=c(16, 1)) + scale_colour_manual("Model", values=c("darkgray", "black"), labels=c("T", "ST")) +
    theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent")) +
    xlab("Scenario") + ylab("Proportion within CI")
  return(p)
}
```

```{r figure-5abc}
cip1 <- getCIProportions(scenarios=scenarios, modelNames=modelNames)
cip2 <- getCIProportions(scenarios=paste0(scenarios, "combined"), modelNames=modelNames)
cip3 <- getCIProportions(scenarios=paste0(scenarios, "10days"), modelNames=modelNames)

p1 <- plotCIProportions(cip1)
saveFigure(p1, "manuscript-figure-5a.png", width=4, height=2)
p2 <- plotCIProportions(cip2)
saveFigure(p2, "manuscript-figure-5b.png", width=4, height=2)
p3 <- plotCIProportions(cip3)
saveFigure(p3, "manuscript-figure-5c.png", width=4, height=2)
```

>>>>

```{r figure-5-init}
getCIProportions <- function(scenarios, modelNames, panel, scenarioNames) {
  study <- getStudy(scenario="A")
  validation <- Validation(study=study, populationSizeOverEstimate=Inf)
  a <- validation$getValidatedCredibilityIntervalsProportions(scenarios=scenarios, modelNames=modelNames)
  b <- validation$getValidatedCredibilityIntervalsProportions(scenarios=scenarios, modelNames=modelNames, probs=c(.25, .75), probsName="50%")
  credibilityIntervals <- rbind(a, b)
  credibilityIntervals$panel <- panel
  credibilityIntervals$scenario <- scenarioNames
  return(credibilityIntervals)  
}

plotCIProportions <- function(credibilityIntervals) {
  p <- ggplot(credibilityIntervals, aes(scenario, Proportion, shape=Interval, colour=modelName)) +
    geom_hline(aes(yintercept=.5), color="grey90") +
    geom_hline(aes(yintercept=.95), color="grey90") +
    geom_point() +
    scale_shape_manual(values=c(16, 1)) + scale_colour_manual("Model", values=c("darkgray", "black"), labels=c("T", "ST")) +
    theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent")) +
    xlab("Scenario") + ylab("Proportion within CI") +
    facet_wrap(~panel) + ylim(0, 1) +
    theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank())
  return(p)
}
```

```{r figure-5abc}
cip1 <- getCIProportions(scenarios=scenarios, modelNames=modelNames, panel="a", scenarioNames=scenarios)
cip2 <- getCIProportions(scenarios=paste0(scenarios, "combined"), modelNames=modelNames, panel="b", scenarioNames=scenarios)
cip3 <- getCIProportions(scenarios=paste0(scenarios, "10days"), modelNames=modelNames, panel="c", scenarioNames=scenarios)
cip <- rbind(cip1, cip2, cip3)
p <- plotCIProportions(cip)
saveFigure(p, "manuscript-figure-5.png", width=6, height=2)

#p1 <- plotCIProportions(cip1)
#saveFigure(p1, "manuscript-figure-5a.png", width=4, height=2)
#p2 <- plotCIProportions(cip2)
#saveFigure(p2, "manuscript-figure-5b.png", width=4, height=2)
#p3 <- plotCIProportions(cip3)
#saveFigure(p3, "manuscript-figure-5c.png", width=4, height=2)
```
